Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2015-11-30 Docs/IJES/journal.tex
Minor changes

In terms of SMT-based verification, most related studies are restricted to present the model, its modification to programming languages ({\it e.g.}, C/C++ and Java), and the application to multi-thread algorithms or to embedded systems to check for program correctness. In~\cite{Ramalho2013} it presents a bounded model checker for C++ programs, which is an evolution of dealing with C programs and~\cite{Cordeiro2012} uses ESBMC for embedded ANSI-C software. In~\cite{Trindade2015} and~\cite{Trindade2016} it was proven that it is possible to use ESBMC to solve HW-SW partitioning in a single- and multi-core way. There are related studies focused on decreasing the verification time of model checkers by applying Swarm Verification ~\cite{Holzmann2011}, and modifications of internal search engines to add support for parallelism ~\cite{Holzmann2012}, but there is still the need for initiatives related to parallel SMT solvers ~\cite{Wintersteiger2009}.

Recently, the SMT solver Z3 has been extended to pose and solve optimization problems modulo theories ~\cite{Bjorner2015}. In particular, 
$\nu$Z tool offers substantial performance improvement in optimization problems~\cite{Bjorner2014,Bjorner2015}. As an application example, \cite{Pavlinovic2015} propose an approach which considers all possible compiler error sources for statically typed fu	nctional programming languages and reports the most useful one subject to some usefulness criterion. The authors formulate this approach as an optimization problem related to SMT and use $\nu$Z to compute an optimal error source in a given ill-typed program. The approach described by \cite{Pavlinovic2015}, which uses MaxSMT solver $\nu$Z, shows a significant performance improvement if compared to previous SMT encodings and localization algorithms.

@@

\bibitem[\protect\citeauthoryear{Arato et al.}{2003}]{Arato2003}
Arato, P., Juhasz, S., Mann, A., Orban, A. and Papp, D. (2003) 'Hardware/software partitioning in embedded system design', {\it International Symposium on Intelligent Signal Processing}, pp.192--202

>>>>

In terms of SMT-based verification, most related studies are restricted to present the model, its modification to programming languages ({\it e.g.}, C/C++ and Java), and the application to multi-thread algorithms or to embedded systems to check for program correctness. In~\cite{Ramalho2013} it presents a bounded model checker for C++ programs, which is an evolution of dealing with C programs and~\cite{Cordeiro2012} uses ESBMC for embedded ANSI-C software. In~\cite{Trindade2015}, and~\cite{Trindade2016} it was proven that it is possible to use ESBMC to solve HW-SW partitioning in a single- and multi-core way. There are related studies focused on decreasing the verification time of model checkers by applying Swarm Verification ~\cite{Holzmann2011}, and modifications of internal search engines to add support for parallelism ~\cite{Holzmann2012}, but there is still the need for initiatives related to parallel SMT solver~\cite{Wintersteiger2009}.

Recently, the SMT solver Z3 has been extended to pose and solve optimization problems modulo theories~\cite{Bjorner2015}. In particular, 
$\nu$Z tool offers substantial performance improvement in optimization problems~\cite{Bjorner2014,Bjorner2015}. As an application example, \cite{Pavlinovic2015} propose an approach which considers all possible compiler error sources for statically typed fu	nctional programming languages and reports the most useful one subject to some usefulness criterion. The authors formulate this approach as an optimization problem related to SMT and use $\nu$Z to compute an optimal error source in a given ill-typed program. The approach described by \cite{Pavlinovic2015}, which uses MaxSMT solver $\nu$Z, shows a significant performance improvement if compared to previous SMT encodings and localization algorithms.

@@

\bibitem[\protect\citeauthoryear{Arato \textit{et al.}}{2003}]{Arato2003}
Arato, P., Juhasz, S., Mann, A., Orban, A. and Papp, D. (2003) 'Hardware/software partitioning in embedded system design', {\it International Symposium on Intelligent Signal Processing}, pp.192--202
